---
output: 
  html_fragment:
    self_contained: false
---


<div class="contents">
## Using the book

### R packages

There are quite a few R packages used in the book.
To prepare your R installation for running *all* the examples in this book, you can use the following commands to install
these packages.

```{r install1, eval=FALSE, tidy=TRUE}
packages <- c(
  "AER", "ca", "car", "colorspace", "corrplot", "countreg", "directlabels", "effects", "ggparallel", "ggplot2", "ggtern", "gmodels", "gnm", "gpairs", "heplots", "Lahman", "lattice", "lmtest", "logmult", "MASS", "mgcv", "nnet", "plyr", "pscl", "RColorBrewer", "reshape2", "rms", "rsm", "sandwich", "splines", "vcd", "vcdExtra", "VGAM", "xtable")
install.packages(packages)
```

The `countreg` package, used in Chapter 11, may not yet be available on [CRAN](http://cran.r-project.org).
If not, you can install it from the R-Forge development site.

```{r install2, eval=FALSE}
# if countreg is not yet on CRAN:
install.packages("countreg", repos="http://R-Forge.R-project.org")
```

### Data sets by package

The following lists the data sets used in the book, by package. Links to the data set documentation
for [CRAN](http://cran.r-project.org) packages are courtesy of http://www.inside-r.org/.

**AER**
:  [NMES1988](http://www.inside-r.org/packages/cran/AER/docs/NMES1988) 

**agridat**
:  [jansen.strawberry](http://www.inside-r.org/packages/cran/agridat/docs/jansen.strawberry) 

**car**
:  [Womenlf](http://www.inside-r.org/packages/cran/car/docs/Womenlf) 

**countreg**
:  CodParasites, CrabSatellites 

**datasets**
:  HairEyeColor, iris, UCBAdmissions 

**effects**
:  [Arrests](http://www.inside-r.org/packages/cran/effects/docs/Arrests) 

**HistData**
:  [Arbuthnot](http://www.inside-r.org/packages/cran/HistData/docs/Arbuthnot) 

**Lahman**
:  [Master](http://www.inside-r.org/packages/cran/Lahman/docs/Master) 

**logmult**
:  [criminal](http://www.inside-r.org/packages/cran/logmult/docs/criminal), [gss8590](http://www.inside-r.org/packages/cran/logmult/docs/gss8590) 

**MASS**
:  [birthwt](http://www.inside-r.org/packages/cran/MASS/docs/birthwt), [caith](http://www.inside-r.org/packages/cran/MASS/docs/caith) 

**Sleuth2**
:  [case2201](http://www.inside-r.org/packages/cran/Sleuth2/docs/case2201) 

**vcd**
:  [Arthritis](http://www.inside-r.org/packages/cran/vcd/docs/Arthritis), [Bundesliga](http://www.inside-r.org/packages/cran/vcd/docs/Bundesliga), [Butterfly](http://www.inside-r.org/packages/cran/vcd/docs/Butterfly), [CoalMiners](http://www.inside-r.org/packages/cran/vcd/docs/CoalMiners), [Employment](http://www.inside-r.org/packages/cran/vcd/docs/Employment), [Federalist](http://www.inside-r.org/packages/cran/vcd/docs/Federalist), [HorseKicks](http://www.inside-r.org/packages/cran/vcd/docs/HorseKicks), [Lifeboats](http://www.inside-r.org/packages/cran/vcd/docs/Lifeboats), [PreSex](http://www.inside-r.org/packages/cran/vcd/docs/PreSex), [Punishment](http://www.inside-r.org/packages/cran/vcd/docs/Punishment), [RepVict](http://www.inside-r.org/packages/cran/vcd/docs/RepVict), [Saxony](http://www.inside-r.org/packages/cran/vcd/docs/Saxony), [SexualFun](http://www.inside-r.org/packages/cran/vcd/docs/SexualFun), [SpaceShuttle](http://www.inside-r.org/packages/cran/vcd/docs/SpaceShuttle), [Suicide](http://www.inside-r.org/packages/cran/vcd/docs/Suicide), [UKSoccer](http://www.inside-r.org/packages/cran/vcd/docs/UKSoccer), [VisualAcuity](http://www.inside-r.org/packages/cran/vcd/docs/VisualAcuity), [WeldonDice](http://www.inside-r.org/packages/cran/vcd/docs/WeldonDice), [WomenQueue](http://www.inside-r.org/packages/cran/vcd/docs/WomenQueue) 

**vcdExtra**
:  [Abortion](http://www.inside-r.org/packages/cran/vcdExtra/docs/Abortion), [Accident](http://www.inside-r.org/packages/cran/vcdExtra/docs/Accident), [AirCrash](http://www.inside-r.org/packages/cran/vcdExtra/docs/AirCrash), [Caesar](http://www.inside-r.org/packages/cran/vcdExtra/docs/Caesar), [Cormorants](http://www.inside-r.org/packages/cran/vcdExtra/docs/Cormorants), [CyclingDeaths](http://www.inside-r.org/packages/cran/vcdExtra/docs/CyclingDeaths), [DaytonSurvey](http://www.inside-r.org/packages/cran/vcdExtra/docs/DaytonSurvey), [Donner](http://www.inside-r.org/packages/cran/vcdExtra/docs/Donner), [Geissler](http://www.inside-r.org/packages/cran/vcdExtra/docs/Geissler), [Hauser79](http://www.inside-r.org/packages/cran/vcdExtra/docs/Hauser79), [ICU](http://www.inside-r.org/packages/cran/vcdExtra/docs/ICU), [Mammograms](http://www.inside-r.org/packages/cran/vcdExtra/docs/Mammograms), [Mental](http://www.inside-r.org/packages/cran/vcdExtra/docs/Mental), [PhdPubs](http://www.inside-r.org/packages/cran/vcdExtra/docs/PhdPubs), [Toxaemia](http://www.inside-r.org/packages/cran/vcdExtra/docs/Toxaemia), [TV](http://www.inside-r.org/packages/cran/vcdExtra/docs/TV), [Vietnam](http://www.inside-r.org/packages/cran/vcdExtra/docs/Vietnam) 

### R code

All of the R code from the book is available in the links below for browsing or saving.  Alternatively
you can get it all in a [zip file](Rcode/DDAR-Rcode.zip).

* [Chapter 2](Rcode/ch02.R)
* [Chapter 3](Rcode/ch03.R)
* [Chapter 4](Rcode/ch04.R)
* [Chapter 5](Rcode/ch05.R)
* [Chapter 6](Rcode/ch06.R)
* [Chapter 7](Rcode/ch07.R)
* [Chapter 8](Rcode/ch08.R)
* [Chapter 9](Rcode/ch09.R)
* [Chapter 10](Rcode/ch10.R)
* [Chapter 11](Rcode/ch11.R)
* [Chapter 12](Rcode/ch12.R)

</div>

